Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-10-21 manuscript/specnet_cssa19.tex
concluding slides added, comments welcome

%\begin{frame}[t]
%\frametitle{Figures}
%\begin{figure}[hb]
%\centering
%\includegraphics[scale=.4]{figures/giniVsLambda.png}
%\caption{The average Gini coefficient of effective wealth (computed pre-Stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income. 500 agents were used in each simulation. The color band represents a bootstrapped 95\% confidence interval.}
%\label{fig:giniVsLambda}
%\end{figure}
%\end{frame}
%
%\begin{frame}[t]
%\frametitle{Figures}
%\begin{figure}[ht]
%\centering
%\includegraphics[scale=.4]{figures/avgLifespanLambda_025.png}
%\caption{Life expectancy comparison between isolates (non-proto members) and
%non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
%The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
%constant agent income to a scenario when the noise is as high as the average.}
%\label{fig:avgLifespanLambda}
%\end{figure}
%\end{frame}
%
%\begin{frame}[t]
%\frametitle{Figures}
%\begin{figure}[ht]
%\centering
%\includegraphics[scale=.4]{figures/avgLifespanLambda2.png}
%\caption{Life expectancy comparison between isolates (non-proto members) and
%non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
%The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
%constant agent income to a scenario when the noise is as high as the average.}
%\label{fig:avgLifespanLambda}
%\end{figure}
%\end{frame}

\begin{frame}[t]
\frametitle{Results}
%% need to link the figures here 
\begin{itemize}
\item Larger environmental noise produces large inequality measures (Figure 4)
\item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figure 5) 
\item Larger connectivity leads to a more egalitarian population
\item Larger connectivity leads to larger separation between the mean lifetimes of the two populations
\end{itemize}

@@

>>>>

\begin{frame}[t]
\frametitle{Figures}
\begin{figure}[hb]
\centering
\includegraphics[scale=.4]{figures/giniVsLambda.png}
\caption{The average Gini coefficient of effective wealth (computed pre-Stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income. 500 agents were used in each simulation. The color band represents a bootstrapped 95\% confidence interval.}
\label{fig:giniVsLambda}
\end{figure}
\end{frame}

\begin{frame}[t]
\frametitle{Figures}
\begin{figure}[ht]
\centering
\includegraphics[scale=.4]{figures/avgLifespanLambda_025.png}
\caption{Life expectancy comparison between isolates (non-proto members) and
non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
constant agent income to a scenario when the noise is as high as the average.}
\label{fig:avgLifespanLambda}
\end{figure}
\end{frame}

\begin{frame}[t]
\frametitle{Figures}
\begin{figure}[ht]
\centering
\includegraphics[scale=.4]{figures/avgLifespanLambda2.png}
\caption{Life expectancy comparison between isolates (non-proto members) and
non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
constant agent income to a scenario when the noise is as high as the average.}
\label{fig:avgLifespanLambda}
\end{figure}
\end{frame}

\begin{frame}[t]
\frametitle{Results}
%% need to link the figures here 
\begin{itemize}
\item Larger environmental noise produces large inequality measures (Figure 1)
\item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figures 2 and 3) 
\item Larger connectivity leads to a more egalitarian population
\item Larger connectivity leads to larger separation between the mean lifetimes of the two populations
\end{itemize}

@@

\begin{frame}[t]
\frametitle{Questions}
\begin{itemize}
\item What are the underlying mechanisms underlying the gap between mean life expectancy of \textit{protos} and \textit{isolates}?
\item Do \textit{protos} of different sizes differ in the mean life expectancy and wealth? 
\item Can we derive the results of these simulations from the defining SDS?
\item Do other baseline network models like \textit{scale-free} and \textit{small-world} models induce similar systematic differences between \textit{protos} and \textit{isolates}?
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Conclusion}
\begin{itemize}
\item These are very preliminary results 
\item Repeating these simulations on other baseline network models might provide more clarity
\item These models might be amenable to mean field analysis 
\end{itemize}
More generally
\begin{itemize}
\item Our models are an useful addition to the variety of dynamical system models on networks 
\item Despite their simplicity, the exhibit interesting dynamics and are useful to study the two-way interaction between structure and dynamics.  
\end{itemize}
\end{frame}
